Recent advances in smartphone computational photography

### 2020-09-17 annotated-bibliography.tex
Updates from Overleaf

\subsection{Background Sources}
\begin{itemize}
\item Hasinof 2016\cite{Hasinoff2016} is cited in both of the previous mentioned articles and describes an earlier multi-frame burst merging algorithm. It is used as a point of comparison by both primary sources and will be necessary background information. It is also from Google Research. I think this could end up being more of a primary source.
\item Barron 2017 \cite{Barron2017} is on the auto-white-balance algorithm used in \cite{Liba2019} and will be used for background information on that.
\item Wikipedia articles \cite{wiki:BayerFilter, wiki:Demosaicing, wiki:Aliasing} provide background information on Bayer filters, demosaicing, and aliasing that are necessary to explain how the algorithm in \cite{Wronski2019} improves on existing techniques.

\item \cite{blog:Wronski2018, blog:Levoy2018} are the blog posts accompanying \cite{Wronski2019, blog:Levoy2018} respectively. They provide additional information and examples of the algorithms.

>>>>

\subsection{Background Sources}
\begin{itemize}
\item Hasinof 2016 \cite{Hasinoff2016} is cited in both of the previous mentioned articles and describes an earlier multi-frame burst merging algorithm. It is used as a point of comparison by both primary sources and will be necessary background information. It is also from Google Research. I think this could end up being more of a primary source.
\item Barron 2017 \cite{Barron2017} is on the auto-white-balance algorithm used in \cite{Liba2019} and will be used for background information on that.
\item Wikipedia articles \cite{wiki:BayerFilter, wiki:Demosaicing, wiki:Aliasing} provide background information on Bayer filters, demosaicing, and aliasing that are necessary to explain how the algorithm in \cite{Wronski2019} improves on existing techniques.

\item \cite{blog:Wronski2018, blog:Levoy2018} are the blog posts accompanying \cite{Wronski2019, Liba2019} respectively. They provide additional information and examples of the algorithms.
